The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-03-23 SC-challenge.tex
reformatted table

\usepackage{color}
\usepackage{xcolor}

\definecolor{blueish}{rgb}{0.2,0.2,0.8}
\newcommand{\katznote}[1]{ {\textcolor{blueish} { ***DSK: #1 }}} % Dan
\newcommand{\knnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}} % Kyle
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}} %Arfon

@@

\begin{table}[!t]
    \tbl{\textbf{Key research challenges and possible solutions/methods. \katznote{formatting help welcome}\label{tab:challenges}}}
    {\begin{tabular}{p{2in}p{3in}}
        \hline
\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\ \hline \hline

Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\ \hline

Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\ \hline

Establish mechanisms for software to cite other software (i.e., dependencies) & \\ \hline

Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\ \hline

Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\ \hline

Increase cultural acceptance of the concept of software as a digital product & \\ 
\hline
    \end{tabular}}
\end{table}

\knnote{suggest ``few possible answers or clear path that might be followed''} \katznote{tried to start in table}

>>>>

\usepackage{booktabs,multicol}

\usepackage{color}
\usepackage[table]{xcolor}

\definecolor{lightgray}{gray}{0.9}
\definecolor{blueish}{rgb}{0.2,0.2,0.8}
\newcommand{\katznote}[1]{ {\textcolor{blueish} { ***DSK: #1 }}} % Dan
\newcommand{\knnote}[1]{ {\textcolor{orange} { ***KEN: #1 }}} % Kyle
\newcommand{\asnote}[1]{ {\textcolor{red} { ***AMS: #1 }}} %Arfon

@@

\rowcolors{2}{}{lightgray}
\begin{table}[htbp]%
\tbl{Key research challenges and possible solutions\slash methods\label{tab:challenges}}{%
\begin{tabular}{@{}p{0.38\linewidth}p{0.58\linewidth}@{}}
\toprule
\textbf{Key research Challenge} & \textbf{Possible solutions/methods} \\
\midrule

Identify necessary metadata associated with software for citation & The CodeMeta project~\cite{CodeMeta} is working to do this now \\

Standardize proper formats for citing software in publications & The FORCE11 Software Citation Working Group is currently working to define and gain community acceptance for software citation principles, after which (starting in April 2016) a follow-on group to implement the software citation principles will likely start, and part of the charge for this group will be to work with publishers on this challenge \\

Establish mechanisms for software to cite other software (i.e., dependencies) & \\

Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem & The FORCE11 software citation implementation working group will also work on this, in collaboration with publishers and indexers \\

Determine standard practices for peer review of software & Professional societies and science communities need to determine how this will happen \\

Increase cultural acceptance of the concept of software as a digital product & \\ 
\bottomrule
\end{tabular}}
\end{table}

\knnote{suggest ``few possible answers or clear path that might be followed''}
